%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Open Source Contributor} % Job title
{Various Projects} % Organization
{Atlanta, GA} % Location
{Nov. 2019 - Present} % Date(s)
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Started contributing to the NodeJS-based WikiJS by fixing bugs, helping users with issues, updating site documentation, and automating builds and Docker container creation. Increased test coverage for project while contributing backend ExpressJS code and Vue components.}
        \item {Submitted documentation fixes to various Microsoft documentation repos while studying C\#, ASP.NET, and PowerShell. }
        \item {Studied Elixir and Ruby programming languages and learned to write scripts in Bash and Perl 6.}
        \item {Set up a homelab consisting of three Dell servers by writing Chef recipes to install self-hosted applications and harden servers.}
    \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {.NET Developer} % Job title
    {SoftTech USA} % Organization
    {Norcross, GA} % Location
    {Sep. 2019 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Automated the creation of test environments using a combination of Puppet Bolt tasks and Powershell scripts.}
        \item {Simplified access to complex, legacy e-commerce systems and product configuration databases by writing new API endpoints in ASP.NET while simultaneously writing requirements for future endpoints required to phase out legacy code components. }
        \item {Refactored generic Entity Framework repositories into domain-driven services responsible for validation of business logic and more flexible transaction support.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Systems Engineering Consultant} % Job title
    {Scott Simontis Consulting} % Organization
    {Atlanta, GA} % Location
    {Apr. 2019 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Reduced page load times from 20+ seconds to 2 seconds for a major online retailer suffering outages during peak sales periods. Identified MySQL index issue responsible for page load issues after adding extensive APM diagnostics.}
        %\item {Performed code reviews, documented data flows & application topology and presented security & operational concerns to executive management while acting as enterprise architect for a client seeking to bring all development operations in-house.}
        \item {Audited codebase inherited by local outbound sales company in preparation for severing ties with their offshore development team. Presented to senior leadership about risks of technical debt, contingency planning, and proposed a new requirements gathering process after demonstrating acute variance between leadership's perception and call center agent perception of productivity improvements attributed to the software.}
        \item {Added Multi-Factor Authentication to Azure Active Directory using ADAL.js and updated an ASP.NET MVC application, REST API and JavaScript Chrome extension to follow new authentication flow.}
        \item {Developed MVP for a social network geared towards primary education faculty that incorporated grading and attendance tracking using ExpressJS, VueJS and SCSS. Designed relational schema for application in PostgreSQL.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Administrator} % Job title
    {Regulatory Affairs Professionals Society} % Organization
    {Rockville, MD} % Location
    {Sep. 2017 - Apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Optimized site performance, resulting in 60 percent drop in page load time and 30 percent drop in bandwidth consumption caused by incorrectly configured CDN and inconsistent HTTP caching.}
		\item {Guided discussions with senior leadership regarding GDPR compliance efforts and automated opt-in mandate by delivering a self-service portal in ReactJS that allowed members to manage their communication preferences and consents.}
		\item {Conducted usability studies using HotJar, user interviews and Google Analytics data to set development priorities for site and demonstrate how technology was advancing business goals and where our conversion funnels were breaking down.}
        \item {Introduced CI concepts to website: Automated front-end asset management with GulpJS, set up build pipeline of CMS backend in Azure DevOps, and began introducing XUnit.NET tests to codebase by refactoring ASP.NET Web Forms pages to comply with MVP pattern.}
        \item {Documented best practices for Application Lifecycle Management and developed runbooks and best practices for content editors.}
        \item {Developed ASP.NET web parts, REST endpoints, C\# services and JavaScript libraries to add new features to Kentico 10 website and integrate with marketing and e-commerce systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Systems Engineer/Development Lead} % Job title
{CFSRES Emergency Systems (defunct)} % Organization
{Remote} % Location
{Jun. 2015 - May. 2017} % Date(s)
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Modified an open-source Software Defined Radio application written in C to publish incoming messages to multiple backend systems via ZeroMQ.}
        \item {Delivered ExpressJS application that streamed real-time emergency dispatches stored in RethinkDB via Socket.io to community residents.}
        \item {Designed PostgreSQL database to maintain subscriber info, forming basis of AWS Simple Notification Service process responsible for sending SMS alerts to subscribers when their station of duty received an incoming page.}
        \item {Deployed and administered AWS LightSail VPS and EC2 instances.}
    \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Consultant} % Job title
    {Intellinet} % Organization
    {Atlanta, GA} % Location
    {Dec. 2013 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Volunteered to serve as Sitecore Knowledge Manager for company; maintained best practices for solution architecture, content hierarchy design, deployments and site launches, routine maintenance, auditing and tuning tasks, and troubleshooting and upgrade procedures. Participated in 3 successful Sitecore MVC implementations.}
        \item {Constructed REST API integration framework to automate API consumption and simplify integration testing, allowing team to respond within a week when client removed an entire layer of their API.}
        \item {Automated Sitecore builds through Gulp task runner and maintained Azure Devops CI/CD pipelines. Wrote deployment runbooks for clients and provided guidance to Operations teams during deployments.}
        \item {Wrote modular, ADA-compliant front-end components using SCSS, jQuery, KnockoutJS and QUnit. Wrote the sandwich customization user interface used by Subway's online ordering system.}
        \item {Created business rules engines, actor frameworks, dynamic SSRS reports and a Lucene-based geographical search engine during ASP.NET MVC application development projects.}
        \item {Implemented C\# batch process to accurately migrate financial records to Great Plains by calling a collection of T-SQL stored procedures. Extended GP functionality by authoring ASP.NET Web API endpoints to support time entry needs and automate payroll processing workflows using Quartz.NET scheduled tasks.}
      \end{cvitems}
    }



%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Applied Information, Inc.} % Organization
    {Suwanee, GA} % Location
    {May. 2012 - Aug. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed a digital billboard system powered by a custom-developed Windows 7 Embedded controller running a C\# service to control sign output and content management functions. Established XML scheduling format and a Cron-inspired algorithm to drive content display. Assembled hardware for prototype units. Integrated GPS receivers, cellular modems and video input capture interfaces with controller software.}
        \item {Supervised an overseas team tasked with porting the advertisement scheduling system to Android, which was delivered on-time and within budget.}
        \item {Debugged digital sign controller failures occurring on Z80 microcontrollers running MicroC RTOS. Performed tests on microcontrollers as needed to investigate failure hypotheses and design more efficient battery power packs.}
        \item {Wrote a batch process to pull data from a SQL data warehouse and develop custom charts for dashboard systems to alert fleet owners of potential mechanical failures and upcoming scheduled maintenance which would require substituting vehicles to avoid any operational impact.}
        \item {Identified a plaintext password storage vulnerability in our cloud monitoring interface and implemented password hashing with BCrypt to protect passwords.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
