%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {B.S. Computer Science (Incomplete)} % Degree
    {Georgia Institute of Technology} % Institution
    {Atlanta, GA} % Location
    {Aug. 2009 - May 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {94 of 126 credit hours completed; left school to become an Emergency Medical Technician.}
        \item {Specializations: Systems and Architecture,  Information Internetworks}
        \item {Participated in Collaborative Workforce undergraduate research program to design a hardware/software setup to capture lectures in high-definition video and stream the content through Ethernet connections. Studied data sheet and reference manual for a TI DaVinci DSP controller to develop a high-level architecture for development efforts. Maintained team wiki knowledge base. Assisted graduate research students with development of C program to display a real-time spectrogram for use as team demo at end of semester.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Emergency Medical Technician Certificate} % Degree
    {Georgia EMS Academy} % Institution
    {Loganville, GA} % Location
    {2013 - 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Completed curriculum required to take the National Registration of Emergency Medical Technicians exam at the Emergency Medical Technician level.}
        \item {Worked 80 hours of clinicals with South Fulton EMS as part of an Advanced Life Support crew.}
        \item {Completed curriculum required to take the National Registration of Emergency Medical Technicians exam at the Advanced Emergency Medical Technician level.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
