%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineering Consultant} % Job title
    {ImagineX Consulting} % Organization
    {Atlanta, GA} % Location
    {2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote unit and integration tests to validate controllers migrated to ASP.NET Core using XUnit.NET, AutoFixture, and Moq.}
        \item {Demonstrated viability of blue-green deployments in Azure DevOps by containerizing ASP.NET Core application and writing automated build service to create container images.}
        \item {Replaced public fileshare on corporate intranet with an Azure Blob Storage implementation responsible for enforcing access control and serving files via one-time use URLs.}
<<<<<<< HEAD
        \item {Provided guidance on network infrastructure, information security and virtualization during initial design sessions for a VPN tunneling and routing service. Wrote technical specifications for cross-platform VPN login client and update manager \& X.509 certificate validation service. Maintained system integration and data flow diagrams.}
        \item {Wrote microservices to compare hardware thumbprints and user identities against a Certificate Revocation List, issue client certificates pending administrative approval, and deliver IPSec configuration information to authorized clients using Express, Keycloak and PostgreSQL. Wrote Docker Compose files to host services and supporting applications until services could be migrated to Kubernetes.}
        \item {Developed .NET Standard library to create and validate X.509 certificates, establish and tear down IPSec-based VPN connections, store encrypted certificates in SQLite, and pull configuration data from SQLite using a custom configuration provider.}
        \item {Created prototype certificate management User Interface for MacOS using Xamarin.Mac and wrote .NET Core hosting integration to support Dependency Injection and Serilog across all platforms.}
=======
        \item {Provided guidance on network infrastructure, information security and virtualization during initial design sessions for a VPN tunneling and routing service. Wrote technical specifications for cross-platform VPN login client and update manager \& X.509 certificate validation service and maintained system diagrams.}
        \item {Wrote client certificate microservices to compare hardware thumbprints and user identities against a Certificate Revocation List, issue certificates pending administrative approval, deliver IPSec configuration information to authorized clients using Express, Keycloak and PostgreSQL. Wrote Docker Compose files to host services and supporting applications until services could be migrated to Kubernetes.}
        \item {Developed .NET Standard library to create and validate X.509 certificates, establish and tear down IPSec-based VPN connections, store encrypted certificates in SQLite, and pull configuration data from SQLite using a custom configuration provider.}
        \item {Created prototype certificate management User Interface for MacOS using Xamarin.Mac and wrote .NET Core hosting integration to support Dependency Injection and Serilog across all platforms.}
        \item {Containerized legacy DurandalJS applications by replacing ASP.NET SSO code with Nginx JavaScript module while updating codebase to support ES6 and optimize RequireJS builds by rewriting Gulpfiles to use Babel and r.js.}
>>>>>>> 41efd2033ed2459a537131db72bbc8fb53300e63
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {.NET Developer} % Job title
    {SoftTech USA} % Organization
    {Norcross, GA} % Location
    {2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Automated creation of test environments using a combination of Puppet Bolt tasks and PowerShell scripts.}
<<<<<<< HEAD
        \item {Simplified access to legacy e-commerce systems and product configuration databases by writing new API endpoints in ASP.NET. Drafted requirements for future endpoints required to phase out all legacy code.}
        \item {Refactored generic Entity Framework repositories into domain-driven services responsible for validation of business logic.}
        \item {Maintained .NET Core-based utilities responsible for running automated test infrastructure, consolidating log files from Azure Blob storage and indexing error entries into an Apache SOLR instance.}
        \item {Provided architecture direction and suggested best practices to largest US client while working on-site to gather requirements, diagnose production issues, and coordinate development between internal, client, and contract developers.}
=======
        \item {Simplified access to complex, legacy e-commerce systems and product configuration databases by writing new API endpoints in ASP.NET while writing requirements for future endpoints required to phase out legacy code components.}
        \item {Refactored generic Entity Framework repositories into domain-driven services responsible for validation of business logic and more flexible transaction support.}
        \item {Maintained .NET Core-based utilities responsible for running automated test infrastructure, consolidating log files from Azure BLOB storage and indexing error entries into an Apache SOLR instance.}
        \item {Maintained Oracle databases and provided troubleshooting to clients performing migrations by customizing migration stored procedures.}
        \item {Provided architecture direction and suggested best practices to largest US client while working on-site to gather requirements, coordinate development with internal, client, and contract developers.}
>>>>>>> 41efd2033ed2459a537131db72bbc8fb53300e63
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Systems Engineering Consultant} % Job title
    {Scott Simontis Consulting} % Organization
    {Atlanta, GA} % Location
    {2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
<<<<<<< HEAD
        \item {Reduced page load times from 20+ seconds to 2 seconds for a major online retailer suffering outages during peak sales periods. Identified MySQL performance issues responsible and PHP memory leaks after adding  APM diagnostics to hosting environment. Reviewed AWS architecture and hardened Linux servers.}
        \item {Developed MVP for a social network geared towards primary education faculty using Express, Vue, SCSS, and PostgreSQL.}
        \item {Wrote a WPF application to generate visualizations based upon simulation data contained in Excel documents.}
=======
        \item {Reduced page load times from 20+ seconds to 2 seconds for a major online retailer suffering outages during peak sales periods. Identified MySQL index issue responsible for page load issues after adding extensive APM diagnostics. Presented infrastructure optimizations and architectural changes to improve.}
        \item {Developed MVP for a social network geared towards primary education faculty that incorporated grading and attendance tracking using ExpressJS, VueJS and SCSS. Designed relational schema for application in PostgreSQL.}
        \item {Wrote WPF application to generate charts from Excel documents recording simulation data in .NET Core.}
>>>>>>> 41efd2033ed2459a537131db72bbc8fb53300e63
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Principal Consultant \& .NET Team Lead} % Job title
    {Intellinet Consulting} % Organization
    {Atlanta, GA} % Location
    {2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
<<<<<<< HEAD
        \item {Served as enterprise architect for local outbound sales company preparing to end offshore development operations. Presented risks of technical debt, incomplete contingency planning, and lack of documentation to senior leadership. Proposed a new requirements gathering process after conducting user interviews and shadowing sessions with call agents.}
        \item {Proposed software architecture to be followed by offshore developers and performed code reviews before integrating code according to GitLab Flow.}
        \item {Automated development environment setup using PowerShell scripts.}
=======
        \item {Audited codebase inherited by local outbound sales company in preparation for severing ties with their offshore development team. Presented to senior leadership about risks of technical debt, contingency planning, and proposed a new requirements gathering process after demonstrating acute variance between leadership’s perception and call center agent perception of productivity improvements attributed to the software.}
        \item {Added Multi-Factor Authentication to Azure Active Directory using ADAL.js and updated an ASP.NET MVC application, REST API and JavaScript Chrome extension to follow new authentication flow.}
        \item {Proposed software architecture to be followed by offshore developers and performed code reviews before integrating code according to GitLab Flow system.}
        \item {Identified potential developers to join team at technology meetups, and led interviewing process for candidates.}
>>>>>>> 41efd2033ed2459a537131db72bbc8fb53300e63
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Administrator \& Software Engineer} % Job title
    {Regulatory Affairs Professionals Society} % Organization
    {Rockville, MD} % Location
    {2017 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Optimized site performance based on performance measurements and analytics data, resulting in 60 percent drop in page load time and 30 percent drop in bandwidth consumption caused by incorrectly configured CDN and inconsistent HTTP caching.}
<<<<<<< HEAD
        \item {Guided discussions with senior leadership regarding GDPR compliance efforts and risks while identifying all Personally Identifiable Information collected by each department and establishing data integrity and retention governance. Automated opt-in mandate by writing a self-service portal in ReactJS communicating with ASP.NET API controllers to allow members to manage communication preferences.}
        \item {Conducted usability studies using HotJar, user interviews and Google Analytics data to set development priorities for site, identifying underperforming conversion funnels, and improve user experience.}
        \item {Introduced DevOps procedures by automating front-end asset management with GulpJS, setting up build pipeline of CMS backend in Azure DevOps, and refactoring ASP.NET Web Forms pages to use MVP pattern to allow unit testing.}
         \item {Documented best practices for Application Lifecycle Management and developed runbooks and best practices for IT department and content editors.}
         \item {Developed ASP.NET web parts, REST APIs, C\# services and JavaScript components in Kentico 10 to add functionality requested by other departments and integrate with marketing, learning management, and e-commerce systems.}
        \item {Supervised and trained content editors and marketing staff on site operations and best practices.}
        \item {Wrote user stories and requirements for contract developers, providing architectual guidance and technical oversight as required. Performed code reviews on all third-party code before deploying to site. Coordinated site migration from Ektron to Kentico by managing agency developers, performing QA and System Requirements Reviews to ensure all requirements were met, and writing migration scripts to transfer user data into new systems.}
=======
        \item {Guided discussions with senior leadership regarding GDPR compliance efforts and risks while identifying all Personally Identifiable Information collected by each department, setting up recommended data integrity and retention limits. Automated opt-in mandate by writing a self-service portal in ReactJS and relevant ASP.NET Web APIs allowing members to manage their communication preferences and consents.}
        \item {Conducted usability studies using HotJar, user interviews and Google Analytics data to set development priorities for site and demonstrate how technology was advancing business goals and where our conversion funnels were breaking down.}
        \item {Introduced DevOps procedures to company website by automating front-end asset management with GulpJS, setting up build pipeline of CMS backend in Azure DevOps, and refactoring ASP.NET Web Forms pages to use MVP pattern to allow for unit testing.}
         \item {Documented best practices for Application Lifecycle Management and developed runbooks and best practices for IT department and content editors.}
         \item {Developed ASP.NET web parts, REST APIs, C# services and JavaScript components in Kentico 10 to add functionality requested by other departments and integrate with marketing, learning management, and e-commerce systems.}
        \item {Supervised and trained content editors and marketing staff on site operations and approved content for final publication.}
        \item {Wrote user stories and requirements for contract developers, providing architectual guidance and technical oversight as required. Performed code reviews on all third-party code before deploying to site. Coordinated site migration from Ektron to Kentico by managing agency developers, performing QA and System Requirements Reviews to ensure all requirements were met, and wrote migration scripts to transfer user data into new systems.}
        \item {Oversaw creation of a PowerBI dashboard for membership reporting. Maintained Azure SQL database and other infrastructure required for reporting, and fixed errors in queries and ETL process to fix discrepancies in data.}
>>>>>>> 41efd2033ed2459a537131db72bbc8fb53300e63
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
<<<<<<< HEAD
    {Lead Developer} % Job title
=======
    {Development Lead} % Job title
>>>>>>> 41efd2033ed2459a537131db72bbc8fb53300e63
    {CFSRES Emergency Systems (defunct)} % Organization
    {Remote} % Location
    {2015 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Modified an open-source Software Defined Radio application written in C to publish incoming messages to multiple backend systems via ZeroMQ.}
<<<<<<< HEAD
        \item {Wrote ExpressJS application that streamed real-time emergency dispatches stored in RethinkDB via Socket.io to community residents.}
        \item {Designed PostgreSQL database to maintain subscriber info and define users to target with AWS Simple Notification Service SMS alerts.}
=======
        \item {Wrote Express application that streamed real-time emergency dispatches stored in RethinkDB via Socket.io to community residents.}
        \item {Designed PostgreSQL database to maintain subscriber info, forming basis of AWS Simple Notification Service process responsible for sending SMS alerts to subscribers when their station of duty received an incoming page.}
>>>>>>> 41efd2033ed2459a537131db72bbc8fb53300e63
        \item {Deployed and administered AWS infrastructure.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consultant} % Job title
    {Intellinet} % Organization
    {Atlanta, GA} % Location
    {2014 -2017 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
<<<<<<< HEAD
        \item {Volunteered to serve as Sitecore Knowledge Manager for company: maintained best practices for solution architecture, content hierarchy design, deployments and site launches, routine maintenance, auditing and tuning tasks, troubleshooting, and upgrade procedures. Participated in 3 successful Sitecore MVC implementations.}
		\item {Constructed REST API integration framework to automate API consumption and serialization, handle errors, and retry submission of commands based on HTTP status code.}
		\item {Automated Sitecore builds through Gulp task runner and maintained Azure Devops CI/CD pipelines. Wrote deployment runbooks for clients and provided guidance to Operations teams during deployments.}
		\item {Wrote modular, ADA-compliant front-end components using SCSS, jQuery, KnockoutJS and QUnit. Created front-end for item customization used by Subway’s online ordering system.}
		\item {Created business rules engines, actor frameworks, dynamic SSRS reports and a Lucene-based geographical search engine during ASP.NET MVC application development projects.}
		\item {Implemented C# batch process to accurately migrate financial records from a proprietary system to Great Plains by calling T-SQL stored procedures. Extended GP functionality by authoring ASP.NET Web API endpoints to support time entry and automate payroll processing workflows using Quartz.NET scheduled tasks.}
=======
        \item {Volunteered to serve as Sitecore Knowledge Manager for company; maintained best practices for solution architecture, content hierarchy design, deployments and site launches, routine maintenance, auditing and tuning tasks, and troubleshooting and upgrade procedures. Participated in 3 successful Sitecore MVC implementations.}
		\item {Constructed REST API integration framework to automate API consumption and simplify integration testing, add error handling and retry algorithm, allowing team to respond within a week when client removed an entire layer of their API.}
		\item {Automated Sitecore builds through Gulp task runner and maintained Azure Devops CI/CD pipelines. Wrote deployment runbooks for clients and provided guidance to Operations teams during deployments}
		\item {Wrote modular, ADA-compliant front-end components using SCSS, jQuery, KnockoutJS and QUnit. Wrote the sandwich customization user interface used by Subway’s online ordering system.}
		\item {Created business rules engines, actor frameworks, dynamic SSRS reports and a Lucene-based geographical search engine during ASP.NET MVC application development projects.}
		\item {Implemented C# batch process to accurately migrate financial records to Great Plains by calling a collection of T-SQL stored procedures. Extended GP functionality by authoring ASP.NET Web API endpoints to support time entry needs and automate payroll processing workflows using Quartz.NET scheduled tasks.}
>>>>>>> 41efd2033ed2459a537131db72bbc8fb53300e63
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Applied Information, Inc.} % Organization
    {Suwanee, GA} % Location
    {2012 - 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
<<<<<<< HEAD
        \item {Developed a Windows Embedded-based digital billboard controller responsible for updating sign output according to content management system. Wrote XML scheduling format schema and algorithm to assemble image queue based on Cron definitions. Selected controller hardware and assembled prototype units. Integrated GPS receivers, cellular modems and video input capture interfaces with controller.}
		\item {Supervised overseas development team by conducting code reviews, performing requirements gap analysis and maintaining work items and bug tickets.}
		\item {Debugged digital sign controller failures occurring on Z80 microcontrollers running MicroC RTOS.}
=======
        \item {Designed a digital billboard system powered by a custom-developed Windows 7 Embedded controller running a C# service to control sign output and content management functions. Established XML scheduling format and a Cron-inspired algorithm to drive content display. Assembled hardware for prototype units. Integrated GPS receivers, cellular modems and video input capture interfaces with controller software.}
		\item {Supervised an overseas team tasked with porting the advertisement scheduling system to Android, which was delivered on-time and within budget.}
		\item {Debugged digital sign controller failures occurring on Z80 microcontrollers running MicroC RTOS. Performed tests on microcontrollers as needed to investigate failure hypotheses and design more efficient battery power packs.}
		\item {Wrote a batch process to pull data from a SQL data warehouse and develop custom charts for dashboard systems to alert fleet owners of potential mechanical failures and upcoming scheduled maintenance which would require substituting vehicles to avoid any operational impact.}
		\item {Identified a plaintext password storage vulnerability in our cloud monitoring interface and implemented password hashing with BCrypt to protect passwords.}
>>>>>>> 41efd2033ed2459a537131db72bbc8fb53300e63
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Co-Op} % Job title
    {Delcan Technologies} % Organization
    {Suwanee, GA} % Location
    {Fall 2010, Summer 2011, Spring 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
<<<<<<< HEAD
        \item {Simplified testing of backend server components and eliminated hardware procurement costs by creating virtual hardware devices simulating traffic and transportation hardware compatible with federal Department of Transportation NTCIP communication and data protocols.}
        \item {Wrote a NTCIP-compliant digital sign emulator which pulled diagnostic data from proprietary vendor devices and created pixel-perfect renderings of messages and graphics created with a custom markup language to upload images controlling output of proprietary displays.}
		\item {Created user interface for in-vehicle electronic dispatch system used by Georgia DoT HERO first responders to queue incidents and digitize paper incident reports and inspection forms.}
=======
        \item {Simplified testing of backend server components and eliminated hardware procurement costs by creating virtual hardware devices designed to simulate traffic and transportation hardware compatible with federal DoT NTCIP standards.}
        \item {Wrote a NTCIP-compliant digital sign emulator for use on Windows embedded devices which pulled diagnostic data from proprietary vendor devices and created pixel-perfect renderings of messages and graphics created with the MULTI markup language so that images could be uploaded to FTP server on signs for display.}
		\item {Created user interface for in-vehicle electronic dispatch system used by Georgia DoT HERO first responders to queue incidents and replace paper forms and incident reports with digital forms.}
		\item {Wrote T-SQL stored procedures to support SSRS reports for snowplow fleet management systems to quantify material usage and miles of roadway plowed to quantify the cost of salting roads. Trained new co-op students in report creation and troubleshooting of existing reports.}
>>>>>>> 41efd2033ed2459a537131db72bbc8fb53300e63
		\item {Created an ASP.NET MVC application which provided control over variable speed limit corridors operated by Oregon DoT. Wrote formal acceptance testing procedures for entire system and tested algorithms responsible for changing speed limits according to lane occupancy, average speed, and traffic volumes.}
		\item {Added new serial port drivers to snowplow data collection system running on Windows Embedded devices and provided technical support and bug fixes to clients. Traveled on-site to install hardware and troubleshoot communication issues and perform electrical diagnostics for clients experiencing major software issues.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
